\section{Introduction}\label{sec:intro}

Automated random testing is a methodology often neglected by 
programmers and software testers because it is deemed as overly
simple. It has, however, advantages over other techniques because 
it is completely unbiased and allows the execution of a high number 
of calls over a short period of time.


The York Extendible Testing Infrastructure (YETI) provides a framework 
for executing random testing sessions in a language agnostic way. At its core lies a testing engine that performs 
calls one after the other on methods picked at random with arguments generated at random.
%
%The main characteristics of 
%YETI is that it supports multiple programming languages through a 
%language-agnostic meta model. Various testing strategies apply
%to all supported languages thanks to a strong decoupling between the 
%strategies used and the programming language binding. 

Oracles are however language-dependent. In the presence of specifications YETI checks 
inconsistencies between the code and the specifications. In the case of 
languages such as .NET, YETI uses code-contracts\footnote{http://research.microsoft.com/en-us/projects/contracts/} as oracles.
In case a precondition of the method under test is violated, then it 
does not interpret it as a failure. In case no precondition is violated, any 
exception can be interpreted as a bug if it is not declared in the documentation. 
If programmers do not use contracts, a testing session of .NET programs with YETI 
is then a robustness test that reports all runtime exceptions. Because .NET does 
not declare runtime exceptions, all triggered must then be compared with exceptions 
declared in the documentation to check whether they were expected or they are faults.
 

Unlike competitors, YETI also supports a graphical user interface that 
allows test engineers to monitor the testing session and modify some 
of its characteristics while testing. 

Section~\ref{sec:implem} describes its current implementation for .NET.
Section~\ref{sec:rw} presents related work.
We eventually conclude in Section~\ref{sec:conc}.
